Comparing vector-based and Bayesian memory models using large-scale datasets:\protect\\User-generated hashtag and tag prediction on Twitter and StackOverflow

### 2016-06-13 writeups/psycMethods/psycMethods.tex
foo

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult (although likely not impossible) to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.

>>>>

Other successful models have shown that higher-level processes such as a user's goals for picking a hashtag, demographics, and specifics about how a hashtag has been used in the past can also influence hashtag use.
\textcite{lin2013bigbirds} showed that there are at least two distinct use cases for hashtags on Twitter: to mark the content (traditional tagging) and to contribute to a specific community that has created a hashtag.
\textcite{yang2012we} found that demographics such as gender, age, and location can influence a user's selected hashtag.
\textcite{denton2015user} found that the growth and lifetime of a hashtag can be influenced by factors such as how often the hashtag was retweeted and the number of followers for a user that used a particular hashtag.
These types of goal-related features, demographic information, and higher-level attributes of previous hashtag use were not directly included in the declarative memory models that were tested for this research.
They were not included because it would be difficult to fit these features into a modeling framework that is constrained to use only declarative memory processes,
and this research focused on measuring differences in model accuracy for two declarative memory models.
Nonetheless many of these higher-level features may indirectly influence a declarative memory model by influencing the specific tags that a user has chosen in the past,
which in turn boosts base-level activation for these previously-chosen tags, which in turn makes it more likely that they are chosen in the future.
